Coherent optical association of single molecules

### 2020-08-14 paper.tex
still early draft...

The pulse sequence for the experiment can be seen in figure (). Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simutaniously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition. Using the tweezer beam for the Raman transition also allow us to maximize the intensity of the Raman beams and minimize the transfer time.

Figure () shows the geometry of the experiment setup. The B field which defines the quantization axis in the experiment is perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.

@@

This excited state used in the Raman transition was measured in our previous experiment using PA to be at $288... GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on previous FB and interaction shift and 4422 bound state data. Theory prediction was at $770... MHz$. \todo{more, mention/cite Jeremy}

@@

\todo{Resonance observed at}
\todo{FWHM of line}

\todo{Rabi flopping}

>>>>

The pulse sequence for the experiment can be seen in figure (). Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simutaniously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition. Using the tweezer beam for the Raman transition also allow us to maximize the intensity of the Raman beams and minimize the transfer time.
\todo{clarify coprop of Raman beam?}

Figure () shows the geometry of the experiment setup. A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.

@@

This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288... GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770... MHz$. \todo{more, mention/cite Jeremy}

@@

We locate the Raman resonance for the atom to molecule transition at $770... MHz$ (figure \todo{}) with a $15 mW$ tweezer at $288... GHz$ which corresponds to a $... GHz$ single photon detuning.
The background level of $...\%$ corresponds to the propability of preparing the two atoms in the relative motional ground state using interaction shift spectroscopy. When the atoms are transfered into molecule by the Raman transition, there is a decrease in the two body survival since the resulting molecule is not directly detected by our imagine step.
\todo{more explanation of detection?}
\todo{FWHM of line??}

B field dependency $... kHz/G$ which agrees with theory prediction of $... kHz/G$.
Dependency on tweezer power $... kHz/mW$, extrapulated to obtain the bare resonance at $0$ tweezer power to be at $... MHz$.

After confirming the creating of the molecule via optical Raman transition, we proceed to verify the coherence of the process. This is done by fixing the Raman frequency on the resonance and scanned the pulse time. figure ... shows the observed Rabi oscillation between the atomic and molecular states. Fitting the data with a decaying Rabi oscillation suggests that $..\%$ of initial ground state atoms are transfered into the molecular state.

\todo{Atomic lifetime}

Combining the frequency and time scan allow us to accurately fit the parameters for the Raman transition.
Raman Rabi frequency
Molecular state lifetime.
The result shows that the decoherence of the Rabi oscillation is caused by finite lifetime of the molecule in the tweezer.
We can directly measure this by \todo{pulse sequence} (figure ...)...

\todo{Lifetime}

\todo{Fitting}
